Global Life Expectancy: Unraveling Health and Economic Determinants (2000-2015)

### 2024-11-28 paper/paper.qmd
inital

```{r}
#| label: fig-expectancy
#| fig-cap: This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries. The graph shows that more developed countries are tend to have higher average of ages than developing countries. 
#| 
#| . The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

modelsummary::modelsummary(
  list(
    "developed model" = model_developed
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(model_developed) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(model_developed) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(model_developed, "trace")

plot(model_developed, "rhat")
```

>>>>

```{r}
#| label: fig-expectancy
#| fig-cap: This histogram shows the distribution of the percentage of life expectancy dividing by the status of countries. The graph shows that more developed countries are tend to have higher average of ages than developing countries. The bimodal nature of the distribution suggests that candidates either receive very high or low support, with few receiving moderate levels of backing.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

#analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

#analysis_data |> 
  #ggplot(aes(x = width, y = length)) +
  #geom_point(alpha = 0.8) +
  #theme_minimal() +
  #labs(x = "Wing width (mm)",
      # y = "Wing length (mm)")
```

@@

#modelsummary::modelsummary(
  #list(
    #"developed model" = #model_developed
  #),
  #statistic = "mad",
  #fmt = 2
#)
```

@@

#pp_check(model_developed) +
  #theme_classic() +
  #theme(legend.position = "bottom")

#posterior_vs_prior(model_developed) +
  #theme_minimal() +
  #scale_color_brewer(palette = "Set1") +
  #theme(legend.position = "bottom") +
  #coord_flip()
```

@@

#plot(model_developed, "trace")

#plot(model_developed, "rhat")
```
